Synthesizing Symmetric Lenses

### 2018-07-04 papers/SymmetricLenses/main.tex
Added concat case in Theorem 4

Similar to the previous case.
\end{enumerate}
\end{proof}
\begin{theorem*}
  $\ProbabilityOf{\Regex}{\String} = \ProbabilityOf{\ToDNFRegex
    \Regex}{\String}$ and $\LanguageOf{\Regex} =
  \LanguageOf{\ToDNFRegexOf{\Regex}}$
\end{theorem*}
\begin{proof}
\begin{enumerate}
\item
$(S = s)$

By definition, $\Downarrow s = \langle ([s],1) \rangle$. The language of $\langle ([s],1) \rangle$ is just $s$ and $P_{\langle ([s], 1) \rangle}(s') = 
\begin{cases}
1 & \text{if } s = s'\\
0 & \text{otherwise}
\end{cases}$ hence $P_{\langle ([s],1) \rangle}(s') = P_s(s')$.
\item
$(S = \varnothing)$

By definition, $\Downarrow \varnothing = \langle \rangle$. The language of $\langle \rangle$ is the empty set, and $P_{\langle \rangle}(s) = 0 = P_{\varnothing}(s)$
\item
$(S = S^{*p})$

By definition, $\Downarrow (S^{*p}) = \langle [\epsilon \cdot (\Downarrow S)^{*p} \cdot \epsilon] \rangle $. By the induction hypothesis, $P_{(\Downarrow S)} = P_{S}$ and $\mathcal{L}(\Downarrow S) = \mathcal{S}$, hence $\mathcal{L}(\Downarrow S) = \mathcal{L}(S)$. Also,
\begin{align*}
P_{[\epsilon \cdot (\Downarrow S)^{*p}] \cdot \epsilon}(s) &= P_{(\Downarrow S)^{*p}}(s)\\
&= \sum_n \sum_{s_1 \cdot \ldots \cdot s_n=s} p^n * (1-p) * \prod_{i=1}^n P_{(\Downarrow S)}(s_i)\\
&= \sum_n \sum_{s_1 \cdot \ldots \cdot s_n=s} p^n * (1-p) * \prod_{i=1}^n P_{S}(s_i)\\
&= P_{S^{*p}}(s)
\end{align*}
\item
$(S = S_1 \cdot S_2)$

By definition, $\Downarrow (S_1 \cdot S_2) = (\Downarrow S_1) \odot (\Downarrow S_2)$. By the induction hypothesis, $\mathcal{L}(S_1) = \mathcal{L}(\Downarrow S_1)$ and $P_{S_1} = P_{(\Downarrow S_1)}$, and $\mathcal{L}(S_2) = \mathcal{L}(\Downarrow S_2)$ and $P_{S_2} = P_{(\Downarrow S_2)}$
\end{enumerate}
\end{proof}
\end{document}

>>>>

Similar to the previous case.
\end{enumerate}
\end{proof}

\begin{theorem*}
  $\ProbabilityOf{\Regex}{\String} = \ProbabilityOf{\ToDNFRegex
    \Regex}{\String}$ and $\LanguageOf{\Regex} =
  \LanguageOf{\ToDNFRegexOf{\Regex}}$
\end{theorem*}
\begin{proof}
By \sam{COPY PASTE PROOF FROM BIJECTIVE LENS PAPER} $\LanguageOf{\Regex} =
  \LanguageOf{\ToDNFRegexOf{\Regex}}$, so we will prove the result $\ProbabilityOf{\Regex}{\String} = \ProbabilityOf{\ToDNFRegex
    \Regex}{\String}$.
\begin{enumerate}
\item
$(S = s)$

By definition, $\Downarrow s = \langle ([s],1) \rangle$ and $P_{\langle ([s], 1) \rangle}(s') = 
\begin{cases}
1 & \text{if } s = s'\\
0 & \text{otherwise}
\end{cases}$ hence $P_{\langle ([s],1) \rangle}(s') = P_s(s')$.
\item
$(S = \varnothing)$

By definition, $\Downarrow \varnothing = \langle \rangle$ and $P_{\langle \rangle}(s) = 0 = P_{\varnothing}(s)$
\item
$(S = S^{*p})$

By definition, $\Downarrow (S^{*p}) = \langle [\epsilon \cdot (\Downarrow S)^{*p} \cdot \epsilon] \rangle $. By the induction hypothesis, $P_{(\Downarrow S)} = P_{S}$, hence
\begin{align*}
P_{[\epsilon \cdot (\Downarrow S)^{*p}] \cdot \epsilon}(s) &= P_{(\Downarrow S)^{*p}}(s)\\
&= \sum_n \sum_{s_1 \cdot \ldots \cdot s_n=s} p^n * (1-p) * \prod_{i=1}^n P_{(\Downarrow S)}(s_i)\\
&= \sum_n \sum_{s_1 \cdot \ldots \cdot s_n=s} p^n * (1-p) * \prod_{i=1}^n P_{S}(s_i)\\
&= P_{S^{*p}}(s)
\end{align*}
\item
$(S = S_1 \cdot S_2)$

By definition, $\Downarrow (S_1 \cdot S_2) = (\Downarrow S_1) \odot (\Downarrow S_2)$. By the induction hypothesis, $P_{S_1} = P_{(\Downarrow S_1)}$, and $P_{S_2} = P_{(\Downarrow S_2)}$. Assume that $\Downarrow S_1 = \langle (SQ_1,p_1) \; | \; \ldots \; | \; (SQ_m, p_n)\rangle$ and $\Downarrow S_2 = \langle (TQ_1,q_1) \; | \; \ldots \; | \; (TQ_n, q_m) \rangle$. Then
\begin{align*}
P_{S_1}(s) &= \sum_{i=1}^n p_i P_{SQ_i}(s)\\
P_{S_1}(s) &= \sum_{j=1}^m q_i P_{TQ_j}(s)\\
\end{align*}
hence
\begin{align*}
P_{S_1 \cdot S_2}(s) &= \sum_{s_1 \cdot s_2 = s} P_{S_1}(s_1)* P_{S_2}(s_2)\\
&= \sum_{s_1 \cdot s_2 = s} \left(\sum_{i=1}^n p_i P_{SQ_i}(s_1)\right)* \left(\sum_{j=1}^m q_i P_{TQ_j}(s_2)\right)\\
&= \sum_{s_1 \cdot s_2 = s} \sum_{i=1}^n \sum_{j=1}^m (p_i * q_j) * (P_{SQ_i}(s_1) *  P_{TQ_j}(s_2))\\
&= \sum_{i=1}^n \sum_{j=1}^m (p_i * q_j)\sum_{s_1 \cdot s_2 = s} (P_{SQ_i}(s_1) *  P_{TQ_j}(s_2))
\end{align*}
By definition,
$\ConcatDNFOf{\DNFOf{(\Sequence_1,\Probability_1)\DNFSep\ldots\DNFSep(\Sequence_n,\Probability_n)}}{\DNFOf{(\SequenceAlt_1,\ProbabilityAlt_1)\DNFSep\ldots\DNFSep(\SequenceAlt_m,\ProbabilityAlt_m)}}=$\\
      $\DNFLeft (\ConcatSequenceOf{\Sequence_1}{\SequenceAlt_1},\Probability_1*\ProbabilityAlt_1)\DNFSep \ldots
      \DNFSep
      (\ConcatSequenceOf{\Sequence_1}{\SequenceAlt_m},\Probability_1*\ProbabilityAlt_m)\DNFSep
      \ldots$\\
      $\DNFSep
      (\ConcatSequenceOf{\Sequence_n}{\SequenceAlt_1},\Probability_n*\ProbabilityAlt_1)\DNFSep
      \ldots \DNFSep
      (\ConcatSequenceOf{\Sequence_n}{\SequenceAlt_m},\Probability_n * \ProbabilityAlt_m) \DNFRight$

where
$$\ConcatSequenceOf{[\String_0\SeqSep\Atom_1\SeqSep\ldots\SeqSep\Atom_n\SeqSep\String_n]}{[\StringAlt_0\SeqSep\AtomAlt_1\SeqSep\ldots\SeqSep\AtomAlt_m\SeqSep\StringAlt_m]}=
  [\String_0\SeqSep\Atom_1\SeqSep\ldots\SeqSep\Atom_n\SeqSep\String_n\Concat\StringAlt_0\SeqSep\AtomAlt_1\SeqSep\ldots\SeqSep\AtomAlt_m\SeqSep\StringAlt_m]$$
Hence
$$P_{\langle (SQ_1, p_1) \; | \; \ldots \; | \;(SQ_n,p_n)\rangle \odot \langle (TQ_1, q_1) \; | \; \ldots \; | \;(TQ_m,q_m)\rangle}(s) = \sum_{i=1}^n \sum_{j=1}^m(p_i * q_j) * P_{SQ_i \odot_{SQ} TQ_j}(s)$$
Since $P_{[s_0 \cdot A_1 \cdot \ldots \cdot A_n \cdot s_n]}(s) = \sum_{s_0 \cdot s'_1 \cdot \ldots \cdot s'_n \cdot s_n = s} \prod_{i=1}^n P_{A_i}(s'i)$, then
\begin{align*}
P_{[s_0 \cdot A_1 \cdot \ldots \cdot A_n \cdot s_n] \odot_{SQ} [t_0 \cdot B_1 \cdot \ldots \cdot B_m \cdot t_m]}(s) &= \sum_{s_0 \cdot s'_1 \cdot \ldots \cdot s'_n \cdot s_n \cdot t_0 \cdot t'_1 \cdot \ldots t'_m \cdot t_m =s } \prod_{i=1}^n P_{A_i}(s'_i) \prod_{j=1}^m P_{B_j}(t'_j)\\
&= \sum_{a \cdot b = s} \sum_{s_0 \cdot s'_1 \cdot \ldots \cdot s'_n \cdot s_n = a} \sum_{t_0 \cdot t'_1 \cdot \ldots \cdot t'_m \cdot t_m = b} \prod_{i=1}^n P_{A_i}(s'_i) \prod_{j=1}^m P_{B_j}(t'_j)\\
& \sum_{a \cdot b = s} \left(\sum_{s_0 \cdot s'_1 \cdot \ldots \cdot s'_n \cdot s_n = a} \prod_{i=1}^n P_{A_i}(s'_i)\right) \left(\sum_{t_0 \cdot t'_1 \cdot \ldots \cdot t'_m \cdot t_m = b} \prod_{j=1}^m P_{B_j}(t'_j)\right)\\
&= \sum_{a \cdot b = s}P_{[s_0 \cdot A_1 \cdot \ldots \cdot A_n \cdot s_n]}(a) * P_{[t_0 \cdot B_1 \cdot \ldots \cdot B_m \cdot t_m]}(b)
\end{align*}
In other words, $P_{SQ \odot_{SQ} TQ}(s) = \sum_{a \cdot b = s}P_{SQ}(a) * P_{TQ}(b)$. Hence, 
\begin{align*}
P_{S_1 \cdot S_2}(s) &= \sum_{i=1}^n \sum_{j=1}^m (p_i * q_j)\sum_{s_1 \cdot s_2 = s} (P_{SQ_i}(s_1) *  P_{TQ_j}(s_2))\\
&= \sum_{i=1}^n \sum_{j=1}^m (p_i * q_j)\sum_{s_1 \cdot s_2 = s} P_{SQ_i \odot_{SQ} TQ_j}(s)\\
&= P_{\langle (SQ_1, p_1) \; | \; \ldots \; | \;(SQ_n,p_n)\rangle \odot \langle (TQ_1, q_1) \; | \; \ldots \; | \;(TQ_m,q_m)\rangle}(s)\\
&= P_{(\Downarrow S_1) \odot (\Downarrow S_2)}(s)
\end{align*}
which is what we wanted to show.
\item
\end{enumerate}
\end{proof}
\end{document}
